### 2023-02-13 README.Rmd
Update doc and bump version [no ci]

To obtain the dependency graph of an R package, use `resolve`

```r
library(rang)
graph <- resolve(pkgs = c("openNLP", "LDAvis", "topicmodels", "quanteda"),
                 snapshot_date = "2020-01-16")
```

>>>>

To obtain the dependency graph of R packages, use `resolve`. Currently, this package supports both CRAN and Github packages.

```r
library(rang)
resolve(pkgs = c("sna", "schochastics/rtoot"), snapshot_date = "2022-11-30")
```

```r
graph <- resolve(pkgs = c("openNLP", "LDAvis", "topicmodels", "quanteda"),
                 snapshot_date = "2020-01-16")
```
